\chapter*{Terminology}
\thispagestyle{plain}			% Supress header 

\begin{itemize}
    \item ROM - Read only memory. A memory which in the context of emulator development contains the game data.
    % \item Boot ROM - A ROM containing the initial boot sequence of a unit. In the context of a Game Boy, the boot sequence where the Nintendo logo is displayed.
  %  \item MVP - Minimum Viable Product, is within Lean Startup\cite{Lean} considered a product which allows a team to collect maximum amount of validated learning about customers with the least effort\cite{Lean}. Within this context another definition could be a bare bones product which still could be considered a complete product. 
    \item RAM - Random access memory. As opposed to ROM, RAM can both be read from and written to. The data stored in RAM is however volatile - the memory stores data only as long as it has power.
   % \item KPI - Key Performance Indicators demonstrate how well and effectively a team is working.
    \item \texttt{0x} - Using the \texttt{0x} prefix indicates that the following value is to be interpreted as a hexadecimal value. For example the value \texttt{0xA0} is to be interpreted as 160.
    \item KiB/MiB - KiB and MiB are used for Kibibyte and Mebibyte, they are of base two and are representing  1024 ($2^{10}$) byte and 1 048 576 ($2^{20}$) byte respectively.
    %Kanske ändra till 0xA0 = $A0_̣{16}$?
    \item I/O - Input/Output, used for describing units handling either input or output, such as a display or keyboard.
    \item Scanline - The process of rendering a row of pixels to the display.
    \item CPU - Central Processing Unit 
    \item PPU - Pixel Processing Unit, responsible for producing pixel data for the Game Boy's LCD.
    \item APU - Audio Processing Unit, responsible for generating audio data.
    \item MMU - Memory Management Unit, responsible for handling memory mapping within the emulator.
    \item Microcontroller - A small computer on a single chip.
    \item Software microcontroller - Software imitating the function of a microcontroller.
    \item Sprite - A 2D bitmap representing an image.
    \item Joypad - A device that connects the user's input with the system. In the context of the Game Boy this refers to four directional buttons and four action buttons.
\end{itemize}

\newpage				% Create empty back of side
\thispagestyle{plain}